\ttitle

### 2015-08-20 Appendices/AppendixExcelMacros.tex
Minor changes - Minor edits to Bodycomp, intro, main and appendix - New appendix file for Access database

\lhead{Appendix B. \emph{Excel VBA For CPET Analysis}} % This is for the header on each page - perhaps a shortened title

\setstretch{1.0}
The following VBA code was written by me to facilitate detailed analysis of large volumes of raw CPET data that would not have been otherwise available from the final report generated for clinical use. Where necessary, I have used information from the MSDN knowledgebase and internet fora to supplement my knowledge of coding.

>>>>

\lhead{Appendix \ref{AppendixExcelMacros}. \emph{Excel VBA For CPET Analysis}} % This is for the header on each page - perhaps a shortened title

\setstretch{1.0}

%------------------------------------------

The following VBA code was written by me to facilitate detailed analysis of large volumes of raw CPET data that would not have been otherwise available from the final report generated for clinical use. Where necessary, I have used information from the MSDN knowledgebase and internet fora to supplement my knowledge of coding.

### 2015-08-20 Chapters/BodyComp.tex
Minor changes - Minor edits to Bodycomp, intro, main and appendix - New appendix file for Access database

\subsection{Calculation of body composition}
Computed tomography of the abdomen, performed as part of the routine preoperative staging, was used to calculate body composition based on previously published and well established methods \parencite{bredella_comparison_2010,shen_total_2004}.

>>>>

\subsection{Calculation of body composition}
\label{sec:bodycomp_calculation}
Computed tomography of the abdomen, performed as part of the routine preoperative staging, was used to calculate body composition based on previously published and well established methods \parencite{bredella_comparison_2010,shen_total_2004}.

### 2015-08-20 Chapters/CRP_Complications.tex
Minor changes - Minor edits to Bodycomp, intro, main and appendix - New appendix file for Access database

\subsection{Statistics}
Mann-Whitney U test was used to compare the distribution of postoperative CRP (as a continuous variable) in patients who had a complication and those who did not. Data are presented as median (inter-quartile range, IQR) unless otherwise specified. Line plots with error bars depicting 95\% confidence intervals are used to depict the trends in CRP over time across different patient groups.

@@

>>>>

\subsection{Statistics}
Mann-Whitney U test was used to compare the distribution of postoperative CRP (as a continuous variable) in patients who had a complication and those who did not. Data are presented as median (inter-quartile range, IQR) unless otherwise specified. Line plots with error bars depicting 95\% confidence intervals were used to depict the trends in CRP over time across different patient groups.

@@

\todo{straatman_predictive_2015 - This is hot-off the press - reference this}

### 2015-08-20 Chapters/Introduction.tex
Minor changes - Minor edits to Bodycomp, intro, main and appendix - New appendix file for Access database

The importance of visceral fat in the incidence and severity of postoperative complications is further emphasised by the finding that excess visceral fat is associated with the the occurence of pancreatic fistula after radical total gastrectomy for gastric cancer. Benns and co-workers reported greater blood loss and increased incidence and severity of postoperative complications in obese patients undergoing surgery compared to non-obese pateints. However, there was no difference in operative time or length of stay in hospital. \parencite{benns_impact_2009}

>>>>

The importance of visceral fat in the incidence and severity of postoperative complications is further emphasised by the finding that excess visceral fat is associated with the the occurrence of pancreatic fistula after radical total gastrectomy for gastric cancer. Benns and co-workers reported greater blood loss and increased incidence and severity of postoperative complications in obese patients undergoing surgery compared to non-obese patients. However, there was no difference in operative time or length of stay in hospital. \parencite{benns_impact_2009}
